\documentclass{article}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{indentfirst}   % Indents first paragraph. change if u want ig
\usepackage{setspace} 
\doublespacing

\begin{document}
\title{\textbf{Intermediate Submission Questions}}
\author{Spencer Hirsch, Thomas Johnson}
\date{\today}

\maketitle

\begin{enumerate}
    \item \textbf{For the I/O input, are we generating a sudoku puzzel and randombly 
    filling it? Or hava a text file containing the sudoku puzzle to be read in and
    solved?}

    Have a text file for input, which your program should read and solve.  
    Have text file(s) for input and solved file(s) as output. 

    \item \textbf{What is the difference between compilation screenshots and the three
    sample-runs screenshots? }

    I wanted to see sample runs with input/outputs as your code runs, in your submission 
    file. Not sure how you do it. In "good old days," it would be a screen shot of 
    command mode runs!

    \item \textbf{Can you elaborate on what the "other description" means? like describing 
    what each function does?}

    Anything you want to tell.

    \item \textbf{For the algorithm, are you expecting a specific kind of algorithm? My
    partner and I plan to use the backtracking algorithm and wanted to see if we're on
    the correct path?}

    \item \textbf{Are we creating valid sudoku puzzles or are we taking already generated 
    sudoku puzzles and determining if they are valid?}

    \item \textbf{Intermediate! Show that your algorithm solves 3 test cases of size 4x4.}
    
    \item \textbf{No reference?! Mention it in case you have written from the scratch.}

\end{enumerate}


\end{document}